### 2008-11-25 doc/sec/SecurityFrameworkofARC1.tex
Put the user manual away from security technical documentation

\newcounter{saveenum}

@@

\newcommand\liststyleWWviiiNumxi{%
\newcommand\liststyleWWviiiNumxii{%
\newcommand\liststyleWWviiiNumxv{%
\newcommand\liststyleWWviiiNumxvi{%
\newcommand\liststyleWWviiiNumxxiv{%

@@

\includegraphics[width=1.4228in,height=0.9098in]{SecurityFrameworkofARC1-img1.jpg}

@@

\bigskip
\clearpage\clearpage\setcounter{page}{1}\pagestyle{Convertiv}

@@

\begin{center}
\begin{minipage}{3.3756in}
{\selectlanguage{english}\color{black}
\ \ class SecHandler \{}

@@

\begin{center}
\begin{minipage}{3.8756in}
{\selectlanguage{english}\color{black}
\ \ class PDP \{}

@@

\includegraphics[width=5.7043in,height=5.6354in]{SecurityFrameworkofARC1-img6.png}

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at TCP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7684599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/localendpoint &
\selectlanguage{english}\color{black} service\_ip[:service\_port]
\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/remoteendpoint &
\selectlanguage{english}\color{black} client\_ip[:client\_port] \\\hline
\end{supertabular}
\end{flushleft}

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at TLS MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7684599in}|}
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/ca &
\selectlanguage{english}\color{black} signer of first certificate in
client{\textquotesingle}s chain\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/chain &
\selectlanguage{english}\color{black} Subject of certificate in
client{\textquotesingle}s chain - multiple items\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/subject &
\selectlanguage{english}\color{black} Subject of last certificate in
client{\textquotesingle}s chain\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/identity &
\selectlanguage{english}\color{black} Subject of last non-proxy
certificate in client{\textquotesingle}s chain\\\hline
\end{supertabular}
\end{flushleft}
\paragraph{HTTP}
{\selectlanguage{english}\upshape\color{black}
Information is collected inside HTTP MCC. The Security Attribute is
stored under name {\textquotesingle}HTTP{\textquotesingle} and exports
ARC Request with following attributes:}

\begin{flushleft}
\bottomcaption{Security Attributes collected at HTTP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7684599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/http/path &
\selectlanguage{english}\color{black} HTTP path without host and port
part\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/http/method &
\selectlanguage{english}\color{black} HTTP method\\\hline
\end{supertabular}
\end{flushleft}
\paragraph{SOAP}
{\selectlanguage{english}\upshape\color{black}
Information is collected inside SOAP MCC. Security Attribute is stored
under name {\textquotesingle}SOAP{\textquotesingle} and exports ARC
Request with following attributes:}

\begin{flushleft}
\bottomcaption{Security Attributes collected at SOAP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7684599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/endpoint &
\selectlanguage{english}\color{black} To element of WS-Addressing
structure\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/operation &
\selectlanguage{english}\color{black} SOAP top level element name
without namespace prefix\\\hline
\selectlanguage{english}\color{black} Context &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/namespace &
\selectlanguage{english}\color{black} Namespace of SOAP top level
element\\\hline
\end{supertabular}
\end{flushleft}
\subsection[Delegation Restrictions]{Delegation Restrictions}
\label{bkm:Ref204009393}\subsubsection[Delegation
Architecture]{Delegation Architecture}
\label{bkm:Ref204009914}{\selectlanguage{english}\upshape\color{black}
In current implementation delegation is achieved through Identity
Delegation implemented using X509 Proxy Certificates as defined in RFC
3820. Client wishing to allow service to act on it{\textquotesingle}s
behalf provides Proxy Certificate to the service using Web Service
based Delegation interface described in Section 6.4}

@@

\liststyleWWviiiNumix
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 1}
\item {\selectlanguage{english}\color{black}
Client contacts service requesting operation DelegateCredentialsInit.
This operation has no arguments.}
\item {\selectlanguage{english}\color{black}
Service responds with DelegateCredentialsInitResponse message with
element TokenRequest. That element contains credentials request
generated by service in Value. Type of request is defined by attribute
Format. Currently only supported format is x509. Along with Value
service provides identifier Id which is used in second step.}
\end{itemize}
\liststyleWWviiiNumx
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 2}
\item {\selectlanguage{english}\color{black}
Client requests UpdateCredentials operation with DelegatedToken
argument. This element contains Value with serialized delegated
credentials and Id which links it to first step. Delegated token
element may also contain multiple Reference elements. Reference refers
to the object which these credentials should be applied to in a way
specific to the service. The DelegatedToken element may also be used
for delegating credentials when Step 2 is combined with other
operations on service in service specific way.}
\item {\selectlanguage{english}\color{black}
Service responds with empty UpdateCredentialsResponse message.}
\end{itemize}
\subsection[Schemas, descriptions and examples]{Schemas, descriptions
and examples}
\label{bkm:Ref204010074}\subsubsection[Authorization
Policy]{Authorization Policy}
\label{bkm:Ref204009564}{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/Policy.xsd}
.}

@@

\subsubsection{SimpleList PDP configuration and Policy Example}
{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/simplelistpdp/SimpleListPDP.xsd}
.}

@@

\subsubsection[Arc PDP configuration and Policy Example]{Arc PDP
configuration and Policy Example}
\label{bkm:Ref204009974}\label{bkm:RefSecarcpdpconfigandpolicy}{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/ArcPDP.xsd}
.}

@@

\subsubsection[Delegation SecHandler Configuration]{Delegation
SecHandler Configuration}
\label{bkm:RefSecdelegsechandleconfig}{\selectlanguage{english}\upshape\color{black}
Below is an example of configuration of Delegation SecHandler inside TLS
MCC component.}

@@

\subsubsection[UsernameToken SecHandler configuration]{UsernameToken
SecHandler configuration}
\label{bkm:RefSecuserametokenconfig}{\selectlanguage{english}\upshape\color{black}
Configuration XML schema with comments available at
\href{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}{\textstyleInternetlink{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTo}}\href{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}{\textstyleInternetlink{kenSH.xsd}}
.}

@@

{\selectlanguage{english}\color{black}
X509Token SecHandler must be configured under SOAP MCC.}

@@

\subsection{User Manual}
{\selectlanguage{english}\color{black}
This section describes how to configure and use SecHandler and PDP
elements included in the ARC1 and provides few examples of the ARC
Policy documents. The target readers are those users who will use the
ARC1 middleware. Currently this section is very short on details. It is
going to be continuously extended. Especially taking user feedback into
account.}

\subsubsection[Authorization SecHandler and PDPs]{Authorization
SecHandler and PDPs}
{\selectlanguage{english}\color{black}
There is a specific Authorization SecHandler (arc.authz) which is
implemented for calling the Policy Decision Points (PDP) and serves as
their container. }

{\selectlanguage{english}\color{black}
Usually the Authorization SecHandler and included PDPs are used on the
service side of communication channel. Although it is also possible to
use them on the client side. All possibilities are achieved by
modifying the configuration file (hereafter mentioned as service.xml)
and possibly providing the authorization policy in a separate file.}

{\selectlanguage{english}\color{black}
Here the {\textquotedblleft}echo{\textquotedblright} test service is
used to explaining the usage, but the explanation applies to other
services as well.}

{\selectlanguage{english}\color{black}
The procedure for configuring Authorization SecHandler in service.xml is
following:}

\liststyleWWviiiNumxi
\begin{enumerate}
\item {\selectlanguage{english}\color{black}
Add the Authorization SecHandler as child element
{\textless}SecHandler/{\textgreater} of
{\textless}Service/{\textgreater} element. }
\end{enumerate}
{\selectlanguage{english}\color{black}
The {\textquotedblleft}name{\textquotedblright} and
{\textquotedblleft}event{\textquotedblright} attribute of
{\textless}SecHandler/{\textgreater} element are both important. The
{\textquotedblleft}name{\textquotedblright} attribute is used for
distinguishing betwenn loaded SecHandler objects. The
{\textquotedblleft}event{\textquotedblright} attribute defines for
which message authorization would be enforced. Usually and reasonably
it is done for {\textquotedblleft}incoming{\textquotedblright}
messages. But some services and other Message Chain components may
define other internal types of messages. For possible values please
refer to documentation of particular Service or MCC. In our particular
case {\textquotedblleft}echo{\textquotedblright} service only supports
{\textquotedblleft}incoming{\textquotedblright} messages for this
purpose.}

\liststyleWWviiiNumxi
\setcounter{saveenum}{\value{enumi}}
\begin{enumerate}
\setcounter{enumi}{\value{saveenum}}
\item {\selectlanguage{english}\color{black}
Add the PDP configuration as \ child element
{\textless}PDP/{\textgreater} under
{\textless}SecHandler/{\textgreater}. Currently there are four usable
PDPs distributed as part of the ARC1 middleware:}
\end{enumerate}
\liststyleWWviiiNumxii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
simplelist.pdp -- compares Subject of user{\textquotesingle}s X509
certificate to those stored in a file.}
\item {\selectlanguage{english}\color{black}
arc.pdp -- compares authorization related information parsed from
message at various processing steps \ to Policy document specified in
configuration of this PDP.}
\item {\selectlanguage{english}\color{black}
pdpservice.invoker - composes the ARC Request, puts request into SOAP
message, and invokes the remote PDP service to get the response SOAP
which includes authorization decision. The PDP service functionality is
similar to arc.pdp.}
\item {\selectlanguage{english}\color{black}
delegation.pdp -- compares authorization related information parsed from
message at various processing steps and Policy document embedded in
proxy certificate used by remote side.}
\end{itemize}
{\selectlanguage{english}\color{black}
Default behavior of Authorization SecHandler is to execute all
configured PDPs sequentially till eithe r one of them fails or all
produced positive results. This behavior may be modified by attribute
{\textquotedblleft}action{\textquotedblright} of
{\textless}PDP/{\textgreater} element.}

{\selectlanguage{english}\upshape\color{black}
The description of PDP configuration and ARC Policy example are
available in Section 7}

\subsubsection[Delegation SecHandler, Delegation PDP and Proxy
Certificate Generation]{Delegation SecHandler, Delegation PDP and Proxy
Certificate Generation}
{\selectlanguage{english}\upshape\color{black}
Delegation SecHandler and Delegation PDP in their current state provide
an infrastructure for limiting capabilities of delegated credentials.
Their collect and process policies attached to X509 Proxy Certificates
respectively. Hence to have delegation restriction working both must be
enabled in configuration of service. Configuration of Delegation
SecHandler is described in section 7.10. }

{\selectlanguage{english}\color{black}
The possible location for Delegation PDP is inside Authorization
SecHandler (arc.authz). Depending on how fine grained policy of
delegated credentials is supposed to be corresponding Authrorization
SecHandler may be attached to different MCCs or directly to Service
component. However, the precondition for using Delegation PDP is that
there must be Delegation SecHandler instantiated earlier in chain.}

{\selectlanguage{english}\color{black}
On the client side, command line utility
{\textquotedblleft}approxy{\textquotedblright} utility can be used to
generate Proxy Certificate with Delegation Policy embedded.}

{\selectlanguage{english}\color{black}
Normally approxy appears in \$ARC\_LOCATION/bin. The usage of approxy is
like:}

{\selectlanguage{english}\color{black}
approxy -P proxy.pem -C cert.pem -K key.pem -c constraints}

{\selectlanguage{english}\color{black}
By using argument {\textquotedbl}-c{\textquotedbl}, some constraints can
be specified for proxy certificate. Currently, the life time can be
limited by using {\textquotedbl}-c validityStart=...{\textquotedbl} and
{\textquotedbl}-c validityEnd=...{\textquotedbl}, {\textquotedbl}-c
validityStart=...{\textquotedbl} and {\textquotedbl}-c
validityPeriod=...{\textquotedbl}. Like for example }

{\selectlanguage{english}\color{black}
{}-c validityStart=2008-05-29T10:20:30Z}

{\selectlanguage{english}\color{black}
{}-c validityEnd=2008-06-29T10:20:30Z}

{\selectlanguage{english}\color{black}
The Delegation Policy can be specified by using {\textquotedbl}-c
proxyPolicyFile=...{\textquotedbl} or {\textquotedbl}-c
proxyPolicy=...{\textquotedbl}. Like }

{\selectlanguage{english}\color{black}
{}-c proxyPolicyFile=delegation\_policy.xml}

{\selectlanguage{english}\upshape\color{black}
The Delegation Policy is the same as the ARC Policy explained in section
7.7. Simple example below renders delegated credentials usable only for
contacting service attached to HTTP communication channel under path
/arex (line 6) \ and allows HTTP operation POST (line 9) on it. }

\liststyleWWviiiNumxv
\begin{enumerate}
\item {\selectlanguage{english}\ttfamily\color{black}
{\textless}?xml version={\textquotedbl}1.0{\textquotedbl}
encoding={\textquotedbl}UTF-8{\textquotedbl}?{\textgreater}}
\item {\selectlanguage{english}\color{black}
\texttt{{\textless}Policy
xmlns={\textquotedbl}}\url{http://www.nordugrid.org/schemas/policy-arc}\texttt{{\textquotedbl}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ PolicyId={\textquotedbl}sm-example:policy1{\textquotedbl}
CombiningAlg={\textquotedbl}Deny-Overrides{\textquotedbl}{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ {\textless}Rule RuleId={\textquotedbl}rule1{\textquotedbl}
Effect={\textquotedbl}Permit{\textquotedbl}{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Resources{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Resource
Type={\textquotedbl}string{\textquotedbl}
AttributeId={\textquotedbl}http://www.nordugrid.org/schemas/policy-arc/types/http/path{\textquotedbl}{\textgreater}/arex{\textless}/Resource{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}/Resources{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Actions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Action
Type={\textquotedbl}string{\textquotedbl}
AttributeId={\textquotedbl}http://www.nordugrid.org/schemas/policy-arc/types/http/method{\textquotedbl}{\textgreater}POST{\textless}/Action{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}/Actions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ {\textless}/Rule{\textgreater}}}
\item {\selectlanguage{english}\ttfamily\color{black}
{\textless}/Policy{\textgreater}}
\end{enumerate}
{\selectlanguage{english}\color{black}
Another example of delegation policy is presented below. This policy
restricts usage of delegated credentials to SOAP operation
CreateActivity (line 5) of Basic Execution Service (BES) [4] namespace
(line 9). Such policy could be embedded into credentials delegated to
high level Brokering service performing Grid job submission to low
level BES on behalf of user.}

\liststyleWWviiiNumxvi
\begin{enumerate}
\item {\selectlanguage{english}\ttfamily\color{black}
{\textless}?xml version={\textquotedbl}1.0{\textquotedbl}
encoding={\textquotedbl}UTF-8{\textquotedbl}?{\textgreater}}
\item {\selectlanguage{english}\ttfamily\color{black}
{\textless}Policy
xmlns={\textquotedbl}http://www.nordugrid.org/schemas/policy-arc{\textquotedbl}
PolicyId={\textquotedbl}sm-example:policy1{\textquotedbl}
CombiningAlg={\textquotedbl}Deny-Overrides{\textquotedbl}{\textgreater}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ {\textless}Rule RuleId={\textquotedbl}rule1{\textquotedbl}
Effect={\textquotedbl}Permit{\textquotedbl}{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Actions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ {\textless}Action
Type={\textquotedbl}string{\textquotedbl}
AttributeId={\textquotedbl}http://www.nordugrid.org/schemas/policy-arc/types/soap/operation{\textquotedbl}{\textgreater}CreateActivity{\textless}/Action{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}/Actions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}Conditions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}Condition{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ \ \ {\textless}Attribute
Type={\textquotedbl}string{\textquotedbl}
AttributeId={\textquotedbl}http://www.nordugrid.org/schemas/policy-arc/types/soap/namespace{\textquotedbl}{\textgreater}http://schemas.ggf.org/bes/2006/08/bes-factory{\textless}/Attribute{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ \ \ {\textless}/Condition{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ \ \ \ {\textless}/Conditions{\textgreater}}}
\item {\selectlanguage{english}\color{black}
\texttt{\ \ \ {\textless}/Rule{\textgreater}}}
\item {\selectlanguage{english}\ttfamily\color{black}
{\textless}/Policy{\textgreater}}
\end{enumerate}
\subsubsection{VOMS Proxy Certificate}
{\selectlanguage{english}\color{black}
The commonly used voms proxy certificate can be used in ARC1 for
authentication as normal proxy certificate, and attribute acquiring in
order to make authorization decision based on attributes.}

{\selectlanguage{english}\color{black}
1.How to create voms proxy certificate}

{\selectlanguage{english}\color{black}
Currently the proxy creation utility in ARC1---arcproxy can not be used
for creating voms proxy certificate because the GSI-based communication
requirement from voms server side has not been supported in ARC1 (ARC1
uses standard SSL/TLS communication). So the way to create voms proxy
certificate is still to use the
{\textquotedblleft}voms-proxy-init{\textquotedblright} utility.}

{\selectlanguage{english}\color{black}
2.How to use voms proxy certificate in ARC1}

{\selectlanguage{english}\color{black}
The attribute certificate (AC, which is created by voms server and then
embedded in voms proxy certificate \ as one of the certificate
extension by {\textquotedblleft}voms-proxy-init{\textquotedblright}
client) \ will be parsed by TLS handling plugin (called MCCTLS) of
ARC1, and saved in the message context in the format
{\textquotedblleft}grantor=knowarc://testvoms.knowarc.eu:50000/knowarc:role=guest{\textquotedblright}.}

{\selectlanguage{english}\color{black}
Service administrator needs to configure the trusted DN chain for
verifying the AC under tls MCC{\textquotesingle}s configurationwith the
following format. You should specify one node
({\textless}tls:VOMSCertTrustDNChain/{\textgreater}) for each vo which
you trust. The reason why using trusted DN chain is for service to
restrict which vo server is trusted. }

{\selectlanguage{english}\color{black}
In the following table, the first
{\textless}tls:VOMSCertTrustDNChain{\textgreater} in the following
table defines two items: the first one is the DN of voms server, the
second line is the DN of the corresponding CA. The second
{\textless}tls:VOMSCertTrustDNChain{\textgreater} defines regular
expression for matching, the DN of voms server and DN of the
corresponding CA should both match it. The third one defines the
external file which includes the
{\textless}tls:VOMSCertTrustDNChain{\textgreater}.}

{\selectlanguage{english}\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDN{\textgreater}/O=Grid/O=NorduGrid/OU=fys.uio.no/CN=ABCDE{\textless}/tls:VOMSCertTrustDN{\textgreater}}

{\selectlanguage{english}\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDN{\textgreater}/O=Grid/O=NorduGrid/CN=NorduGrid
Certification Authority{\textless}/tls:VOMSCertTrustDN{\textgreater}}

{\selectlanguage{english}\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}/tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustDNChain{\textgreater}}

{\selectlanguage{english}\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ \ \ {\textless}tls:VOMSCertTrustRegex{\textgreater}\^{}/O=Grid/O=NorduGrid{\textless}/tls:VOMSCertTrustRegex{\textgreater}}

{\selectlanguage{english}\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}/tls:VOMSCertTrustDNChain{\textgreater}}

>>>>

@@

@@

\includegraphics[width=1.422in,height=0.9091in]{SecurityFrameworkofARC1-img1.jpg}

@@

\bigskip
\clearpage\clearpage\setcounter{page}{1}\pagestyle{Convertv}

@@

\begin{center}
\begin{minipage}{3.3752in}
{\selectlanguage{english}\color{black}
\ \ class SecHandler \{}

@@

\begin{center}
\begin{minipage}{3.8752in}
{\selectlanguage{english}\color{black}
\ \ class PDP \{}

@@

\includegraphics[width=5.9709in,height=6.3957in]{SecurityFrameworkofARC1-img6.png}

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at TCP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/localendpoint &
\selectlanguage{english}\color{black} service\_ip[:service\_port]
\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/remoteendpoint &
\selectlanguage{english}\color{black} client\_ip[:client\_port] \\\hline
\end{supertabular}
\end{flushleft}

@@

\begin{flushleft}
\bottomcaption{Security Attributes collected at TLS MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/ca &
\selectlanguage{english}\color{black} signer of first certificate in
client{\textquotesingle}s chain\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/chain &
\selectlanguage{english}\color{black} Subject of certificate in
client{\textquotesingle}s chain - multiple items\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/subject &
\selectlanguage{english}\color{black} Subject of last certificate in
client{\textquotesingle}s chain\\\hline
\selectlanguage{english}\color{black} SubjectAttribute &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/tls/identity &
\selectlanguage{english}\color{black} Subject of last non-proxy
certificate in client{\textquotesingle}s chain\\\hline
\end{supertabular}
\end{flushleft}
\paragraph{HTTP}
{\selectlanguage{english}\upshape\color{black}
Information is collected inside HTTP MCC. The Security Attribute is
stored under name {\textquotesingle}HTTP{\textquotesingle} and exports
ARC Request with following attributes:}

\begin{flushleft}
\bottomcaption{Security Attributes collected at HTTP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/http/path &
\selectlanguage{english}\color{black} HTTP path without host and port
part\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/http/method &
\selectlanguage{english}\color{black} HTTP method\\\hline
\end{supertabular}
\end{flushleft}
\paragraph{SOAP}
{\selectlanguage{english}\upshape\color{black}
Information is collected inside SOAP MCC. Security Attribute is stored
under name {\textquotesingle}SOAP{\textquotesingle} and exports ARC
Request with following attributes:}

\begin{flushleft}
\bottomcaption{Security Attributes collected at SOAP MCC}
\tablehead{\hline
\centering \selectlanguage{english}\bfseries\itshape\color{black}
Element &
\centering \selectlanguage{english}\bfseries\itshape\color{black}
AttributeId &
\centering\arraybslash
\selectlanguage{english}\bfseries\itshape\color{black}
Content\\\hline}\begin{supertabular}{|m{1.2330599in}|m{2.5476599in}|m{1.7698599in}|}
\selectlanguage{english}\color{black} Resource &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/endpoint &
\selectlanguage{english}\color{black} To element of WS-Addressing
structure\\\hline
\selectlanguage{english}\color{black} Action &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/operation &
\selectlanguage{english}\color{black} SOAP top level element name
without namespace prefix\\\hline
\selectlanguage{english}\color{black} Context &
\selectlanguage{english}\color{black}
http://www.nordugrid.org/schemas/policy-arc/types/soap/namespace &
\selectlanguage{english}\color{black} Namespace of SOAP top level
element\\\hline
\end{supertabular}
\end{flushleft}
\subsection[Delegation Restrictions]{Delegation Restrictions}
\label{bkm:Ref204009393}\subsubsection[Delegation
Architecture]{Delegation Architecture}
\label{bkm:Ref204009914}{\selectlanguage{english}\upshape\color{black}
In current implementation delegation is achieved through Identity
Delegation implemented using X509 Proxy Certificates as defined in RFC
3820. Client wishing to allow service to act on it{\textquotesingle}s
behalf provides Proxy Certificate to the service using Web Service
based Delegation interface described in Section 6.4}

@@

\liststyleWWviiiNumix
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 1}
\item {\selectlanguage{english}\color{black}
Client contacts service requesting operation DelegateCredentialsInit.
This operation has no arguments.}
\item {\selectlanguage{english}\color{black}
Service responds with DelegateCredentialsInitResponse message with
element TokenRequest. That element contains credentials request
generated by service in Value. Type of request is defined by attribute
Format. Currently only supported format is x509. Along with Value
service provides identifier Id which is used in second step.}
\end{itemize}
\liststyleWWviiiNumx
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Step 2}
\item {\selectlanguage{english}\color{black}
Client requests UpdateCredentials operation with DelegatedToken
argument. This element contains Value with serialized delegated
credentials and Id which links it to first step. Delegated token
element may also contain multiple Reference elements. Reference refers
to the object which these credentials should be applied to in a way
specific to the service. The DelegatedToken element may also be used
for delegating credentials when Step 2 is combined with other
operations on service in service specific way.}
\item {\selectlanguage{english}\color{black}
Service responds with empty UpdateCredentialsResponse message.}
\end{itemize}
\subsection[Schemas, descriptions and examples]{Schemas, descriptions
and examples}
\subsubsection[Authorization Policy]{Authorization Policy}
\label{bkm:Ref204009564}{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/Policy.xsd}
.}

@@

\subsubsection{SimpleList PDP configuration and Policy Example}
{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\href{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/simplelistpdp/SimpleListPDP.xsd}{\textstyleInternetlink{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/simplelistpdp/SimpleListPDP.}}\href{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/simplelistpdp/SimpleListPDP.xsd}{\textstyleInternetlink{xsd}}
.}

@@

\subsubsection[Arc PDP configuration and Policy Example]{Arc PDP
configuration and Policy Example}
\label{bkm:Ref204009974}{\selectlanguage{english}\upshape\color{black}
XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/ArcPDP.xsd}
.}

@@

\subsubsection[Delegation SecHandler Configuration]{Delegation
SecHandler Configuration}
{\selectlanguage{english}\upshape\color{black}
Below is an example of configuration of Delegation SecHandler inside TLS
MCC component.}

@@

\subsubsection[UsernameToken SecHandler configuration]{UsernameToken
SecHandler configuration}
{\selectlanguage{english}\upshape\color{black}
Configuration XML schema with comments available at
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/usernametokensh/UsernameTokenSH.xsd}
.}

@@

{\selectlanguage{english}\upshape\color{black}
X509Token SecHandler must be configured under SOAP MCC.}

@@
